% TODO: Add comment
% 
% Author: Entzian
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\title{MaizeAnalysisAction: 1116BA \tabularnewline \vspace{10 mm} \large{Experiment coordinator: Klukas, Dr. Christian (BA)}}

\author{Automated image analysis report by\tabularnewline Research
	Group Image Analysis - IPK-Gatersleben\tabularnewline \tabularnewline C. Klukas
	\& A. Entzian}

\date{\today ~(\currenttime )}

\maketitle
\thispagestyle{empty}  
\begin{abstract}
This document is automatically created based on the automated image analysis performed 
inside the integrated analysis platform IAP. Currently the pipelines and data analysis tools are in beta status, 
which means that we are working on makeing the analysis procedures, statistical operations, diagram output and report
generation more stable and suitable to the needs of any user of the automated imaging infrastructure at the IPK.

If you have any hints, comments or suggestions for improvements, please don't hesitate to contact any member
		of the group image analysis.
		\end{abstract}
		\vfill
		\small{\textit{E-mail address:} klukas@ipk-gatersleben.de, entzian@ipk-gatersleben.de}
		\newline 
		\small{\textit{Key words and phrases:} image analysis, phenotyping, \textit{Arabidopsis}, barley, maize }
		
		\addtocounter{page}{-1}
		\clearpage
		\tableofcontents
		
		\clearpage
		\pagestyle{headings}
		\section{Experiment info} 
		\subsection{Experiment properties}
		\begin{center}
		\begin{tabular}{|p{3cm}|p{13cm}|}
		\hline
		{\textbf{Experiment}} & MaizeAnalysisAction: 1116BA\tabularnewline
		\hline
		\hline
		{\textbf{Start}} & 10.07.12 07:06\tabularnewline
		\hline
		{\textbf{End}} & 13.06.11 20:58\tabularnewline
		\hline
		{\textbf{Numeric values}} & 8124882 \tabularnewline
		\hline
		{\textbf{Images}} & 70402 \tabularnewline
		\hline
		{\textbf{Storage}} & 11 GB \tabularnewline
		\hline
		{\textbf{Sequence}} & ZEA 3606 \tabularnewline
		\hline
		{\textbf{Defined Outliers}} &  \tabularnewline
		\hline
		\hline 
		\end{tabular}
		\end{center}
		
		\subsection{Remarks}
		\begin{center}
		\begin{tabular}{|p{16.5cm}|}
		\hline 
		{\textbf{Notes}}\tabularnewline
		\hline 
		\hline 
		Snapshot creators: entzian;klukas;muecke \tabularnewline IAP image analysis release R35\textunderscore 2012-06-28\textunderscore release\textunderscore test4 \tabularnewline 26 compute tasks finished \tabularnewline 26 jobs scheduled at  02.07.12 12:05 \tabularnewline processing time: 1 week and 4 days \tabularnewline finished: 14.07.12 04:24\tabularnewline
		\hline
		\hline  
		\end{tabular}
		\end{center}
		
		
		\resetBoolean
		\checkFileNoReset{conditionsFirstFilter.tex}{}{}
		\checkFileNoReset{conditionsSecondFilter.tex}{}{}
		\ifthenelse{\boolean{isFile1}}{
		\subsection{Grouping of selected experiment factors}
		\checkFile{conditionsFirstFilter.tex}{conditionsSecondFilter.tex}{}
		\ifthenelse{\boolean{isFile1} \and \boolean{isFile2}}{
		\subsubsection{Primary filter}
		\begin{center}
		\loadTex{conditionsFirstFilter}
		\end{center}
		
		\subsubsection{Secondary filter}
		\begin{center}
		\loadTex{conditionsSecondFilter}
		\end{center}
		}{
		\ifthenelse{\boolean{isFile1}}{
		\begin{center}
		\loadTex{conditionsFirstFilter}
		\end{center}
		}{
		\begin{center}
		\loadTex{conditionsSecondFilter}
		\end{center}	
		}
		}
		}
		
		\subsection{Full list of experiment factors}
		\begin{center}
		\begin{longtable}{|p{0.7cm}|p{2.2cm}|p{2.2cm}|p{2.2cm}|p{2.2cm}|p{2.2cm}|}
		%|p{2.2cm}
		
		%This is the header for the first page of the table...
		
		\hline
		{\textbf{ID}} & 
		{\textbf{Species}} & 
		{\textbf{Genotype}} & 
		{\textbf{Variety}} &
		{\textbf{Treatment}} & 
		% 	{\textbf{Sequence}} & 
		{\textbf{Growth conditions}}
		\tabularnewline
		\hline
		\hline
		\endfirsthead
		
		%This is the header for the remaining page(s) of the table...
		
		\hline
		{\textbf{ID}} & 
		{\textbf{Species}} & 
		{\textbf{Genotype}} & 
		{\textbf{Variety}} &
		{\textbf{Treatment}} & 
		% 	{\textbf{Sequence}} & 
		{\textbf{Growth conditions}}
		\tabularnewline
		\hline
		\hline
		\endhead
		
		%This is the footer for all pages except the last page of the table...
		
		\multicolumn{6}{l}{{Continued on Next Page\ldots}} 
		\tabularnewline
		\endfoot
		
		%This is the footer for the last page of the table...
		
		\hline \hline
		\endlastfoot
		
		0 & Aromatnaja & Zea mays L. convar. saccharata Koern. var. flavodulcis Koern. & Sowjetunion & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Aromatnaja & Zea mays L. convar. saccharata Koern. var. flavodulcis Koern. & Sowjetunion & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Athletico & S 280 & Deutschland & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Athletico & S 280 & Deutschland & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Athletico & S 280 & Deutschland & wet & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Breslau II & Zea mays L. convar. mays var. rubra Bonaf. & Polen & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Breslau II & Zea mays L. convar. mays var. rubra Bonaf. & Polen & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Col/Chung Nam Jusan/2620 & Zea mays L. & Koreanische DVR & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Col/Chung Nam Jusan/2620 & Zea mays L. & Koreanische DVR & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Cukrova Cervena & Zea mays L. convar. saccharata Koern. & & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Cukrova Cervena & Zea mays L. convar. saccharata Koern. & & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Fernandez & S 250 & Deutschland & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Fernandez & S 250 & Deutschland & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Fernandez & S 250 & Deutschland & wet & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Gelber Badischer Landmais & Zea mays L. convar. mays var. mays & Deutschland & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Gelber Badischer Landmais & Zea mays L. convar. mays var. mays & Deutschland & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Inrafrueh & Zea mays L. convar. dentiformis Koern. var. flavorubra Koern. & & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Inrafrueh & Zea mays L. convar. dentiformis Koern. var. flavorubra Koern. & & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Lester Phister & Zea mays L. convar. dentiformis Koern. var. flavorubra Koern. & Rumaenien & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Lester Phister & Zea mays L. convar. dentiformis Koern. var. flavorubra Koern. & Rumaenien & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Meirenhuang & Zea sp. & China & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Meirenhuang & Zea sp. & China & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Rainbow Amerindian & Zea mays L. convar. microsperma Koern. & & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Rainbow Amerindian & Zea mays L. convar. microsperma Koern. & & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Risovaja 645 & Zea mays L. convar. microsperma Koern. var. oryzoides Koern. & Sowjetunion & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Risovaja 645 & Zea mays L. convar. microsperma Koern. var. oryzoides Koern. & Sowjetunion & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Schindelmeiser & Zea mays L. convar. mays var. mays & Deutschland & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Schindelmeiser & Zea mays L. convar. mays var. mays & Deutschland & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Strenzfelder & Zea mays L. convar. mays var. mays & Deutschland & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Strenzfelder & Zea mays L. convar. mays var. mays & Deutschland & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Taos Pueblo Blue & Zea mays L. convar. mays var. caesia Alef. & USA & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Taos Pueblo Blue & Zea mays L. convar. mays var. caesia Alef. & USA & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Weisse Zarin & Zea mays L. convar. dentiformis Koern. var. leucodon Alef. & Georgien & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & Weisse Zarin & Zea mays L. convar. dentiformis Koern. var. leucodon Alef. & Georgien & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & brona & Zea mays L. convar. dentiformis Koern. var. flavorubra Koern. & Spanien & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & brona & Zea mays L. convar. dentiformis Koern. var. flavorubra Koern. & Spanien & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & lazuti & Zea mays L. convar. aorista Greb. & Georgien & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & lazuti & Zea mays L. convar. aorista Greb. & Georgien & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & miser i bardeti & Zea mays L. convar. mays var. alba Alef. & Albanien & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & miser i bardeti & Zea mays L. convar. mays var. alba Alef. & Albanien & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L & Kuba & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. & Albanien & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. & Albanien & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. & Italien & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. & Italien & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. aorista Greb. & Griechenland & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. aorista Greb. & Griechenland & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. aorista Greb. & Italien & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. aorista Greb. & Italien & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. aorista Greb. & Italien & wet & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. aorista Greb. & Kroatien & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. aorista Greb. & Kroatien & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. dentiformis Koern. & Albanien & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. dentiformis Koern. & Albanien & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. dentiformis Koern. var. flavorubra Koern. & Koreanische DVR & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. dentiformis Koern. var. flavorubra Koern. & Koreanische DVR & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. dentiformis Koern. var. xantodon Alef. & Makedonien & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. dentiformis Koern. var. xantodon Alef. & Makedonien & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. dentiformis Koern. var. xantodon Alef. & Tschechische Republik & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. dentiformis Koern. var. xantodon Alef. & Tschechische Republik & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. mays var. alba Alef. & oesterreich & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. mays var. alba Alef. & oesterreich & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. mays var. aurantiaca Kuleshov \& Kozhukhov & Koreanische DVR & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. mays var. aurantiaca Kuleshov \& Kozhukhov & Koreanische DVR & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. mays var. aurantiaca Kuleshov \& Kozhukhov & Rumaenien & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. mays var. aurantiaca Kuleshov \& Kozhukhov & Rumaenien & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. mays var. mays & Libyen & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. mays var. mays & Libyen & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. mays var. mays & Slowakei & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. mays var. mays & Slowakei & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. mays var. mays & Ungarn & dry & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & Zea mays L. convar. mays var. mays & Ungarn & normal & Maize\textunderscore 1\textunderscore in\textunderscore 4 \tabularnewline \hline
0 & unspecified & unspecified & & control & \tabularnewline \hline
		
		\end{longtable}
		\end{center}
